Gaussian Processes Autoregressive Models for Forecasting the Disturbance Storm Time Index

### 2016-05-23 swsc.tex
Updates from ShareLaTeX

@@

With respect to the \emph{TL} model one important caveat must be noted. The training of the \emph{TL} model was done on Omni data from 1996-2002 which overlaps with a large number of the storm events, therefore the experimental procedure has a strong bias towards \emph{TL} model.

>>>>

\begin{figure}
   \centering
   \includegraphics[width=\textwidth]{energyLandscape.png}
      \caption{Contour plot of model selection metric (\emph{RMSE}) for \emph{GP-ARX} over the validation data.}
         \label{fig:energy}
   \end{figure}

@@

With respect to the \emph{TL} model one important caveat must be noted. The training of the \emph{TL} model was performed on the OMNI data from 1996-2002 which overlaps with a large number of the storm events, therefore the experimental procedure has a strong bias towards \emph{TL} model.
